% This is a basic Math Paper

\documentclass[11pt]{article}
 
% Preamble

\usepackage[margin=1in]{geometry}
\usepackage{amsfonts, amsmath, amssymb}
\usepackage{fancyhdr, float, graphicx}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{fouriernc} % Use the New Century Schoolbook font
\usepackage[nottoc, notlot, notlof]{tocbibind}
\usepackage{url}

% Header and Footer
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\textit{\Large{Operating Systems}}}
%\fancyhead[R]{\textit{something}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{1pt}



% Other Doc Editing
% \parindent 0ex
%\renewcommand{\baselinestretch}{1.5}

\begin{document}

\begin{titlepage}
	\centering

	%---------------------------NAMES-------------------------------

	\huge\textsc{
		MIT World Peace University
	}\\

	\vspace{0.75\baselineskip} % space after Uni Name

	\LARGE{
		Computer Networks\\
		Second Year B.Tech Semister 3\\
		Academic Year 2022-23
	}

	\vfill % space after Sub Name

	%--------------------------TITLE-------------------------------

	\rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt}
	\rule{\textwidth}{0.6pt}
	\vspace{0.75\baselineskip} % Whitespace above the title



	\huge{\textsc{
			Operating Systems
		}} \\



	\vspace{0.5\baselineskip} % Whitespace below the title
	\rule{\textwidth}{0.6pt}\vspace*{-\baselineskip}\vspace*{2.8pt}
	\rule{\textwidth}{1.6pt}

	\vspace{1\baselineskip} % Whitespace after the title block

	%--------------------------SUBTITLE --------------------------	

	\LARGE\textsc{
		Notes from Tananbaum and Classes
	} % Subtitle or further description
	\vfill

	%--------------------------AUTHOR-------------------------------

	Prepared By
	\vspace{0.5\baselineskip} % Whitespace before the editors

	\Large{
		P34. Krishnaraj Thadesar\\
		\vspace{1cm}
		Batch A2
	}


	\vspace{0.5\baselineskip} % Whitespace below the editor list
	\today

\end{titlepage}

\clearpage
\tableofcontents
\clearpage


\section{Processes}

A process is an instance of a program in exeuction. It is an entity that can be assigned to and executed on a procesor.

\begin{enumerate}
	\item Process is compromised of Program Code
	\item Data
	\item Stack
	\item A number of attribute describing the state of process.
\end{enumerate}

\subsection{Process states}
\begin{enumerate}
	\item New
	\item Ready
	\item Running
	\item Waiting
	\item Terminated
	\item Suspended
\end{enumerate}


\subsubsection{Suspended State}
\begin{itemize}
	\item Process is faster than IO so man processes could be waiting for IO
	\item Swap this proces to disk (SSD/ HDD) to free up RAM memory.
	\item Ready or waiting state becomes suspended state when swapped to disk.
\end{itemize}

\section{Process Control Block}
It is a data structure maintained by the Operating System. It holds all necessary information related to Process.
Information Associated with each process is as follows:
\begin{enumerate}
	\item Process state
	\item Program Counter
	\item CPU Registers
	\item CPU Scheduling information
	\item Memory Management Information
	\item Accounting Information
	\item IO Status information
\end{enumerate}

\section{Switches}
\subsection{Context Switches}
\begin{enumerate}
	\item It switches the execution of a process to another, so for that it has to do some stuff,
	\item It saves the state of the first program, and then reloads the state of the next one.
	\item And only then it runs the next process. This takes time, and is a major disadvantage.
	\item It is a mode switch, but a mode switch isnt a context switch.
	\item It is a mode switch coz it requires you to switch mode from user to kernel.
\end{enumerate}

\section{Process Execution}
Consider three processes being executed, all are in the meory, plus the dispatcher.
\paragraph{Dispatcher}
Dispatcher is a small program which switches from one program to another. -

\section{Process Creation}
When a new process is created, the following happens:
\begin{enumerate}
	\item Allocates space to the process in memory
	\item Assign a unique Process ID to the Process
	\item A process control Block PCB gets associated with the process
	\item OS Maintains pointers to each process's PCB in a process table sothat it can access the PCB quickly.
\end{enumerate}

Reasons to create a Process
\begin{enumerate}
	\item New User Job
	\item Created by OS to provide a service
	\item Spawned by existing Process: The action of creating a new process at the explicit request of another process is called process spawning.
\end{enumerate}

After Creation
\begin{enumerate}
	\item Stay in the parent Process
	\item Transfer Control to the child process. The system call for that is called Fork. This child process inherits everything from the parent.
	\item Transfer control to another process.
\end{enumerate}


\subsection{fork()}
A system call fork() is used to create processes. It takes no arguments and returns a process ID.
The syntax for the fork system call
pid = fork();\\
in the Parent process, pid is the child process\\
In the child process, pid is 0

\begin{enumerate}
	\item It allocates a slot in the process table for the new process
	\item It assigns a unique ID number to the child process
	\item It makes a copy of the context of the parent process.
	\item It returns the ID number of the child to the parent process, and a 0 value to the child process process is assigned.
	\item It doesnt take any arguements
	\item Purpose of fork is to create a new process, which becomes the child process of the caller.
	\item After a process is created, both processes will execute the next instruction following the fork system call.
	\item To distinguist the parent from the child, the returned value of fork can be used.
	\item \begin{itemize}
		      \item fork() returns a negative value to the parent if the creation of the child process wasnt successful
		      \item 0 to the child process if successful, and the PID of thus generated child process to the parent process.
	      \end{itemize}
	\item Returned process id is of type PID defined in sys/types.h
	\item Process can se function getpid() to retrieve the process ID assigned to this process.
	\item Linux would make an exact copy of the parent's address space and give it to the child. Therefore the parent and child process will always have a separate address space.

\end{enumerate}

The OS will make two identical copies of address spaces for parent and child processes. So the parent and child processes have different address spaces.
A local variable is:
\begin{enumerate}
	\item Declared inside the process
	\item  Created when the process starts
	\item  Lost when the process terminates
\end{enumerate}

A global variable is:
\begin{enumerate}
	\item Declared outside the process
	\item Created as the process starts
	\item Lost when the program ends
\end{enumerate}

The process ID, i.e., PID of the child process created, is returned to the parent process. (In case of failure, -1 is returned to the parent process.) \\
Zero is returned to the child process. (If it fails, the child process is not created.) If a child process exits at that instant or is interrupted, a signal SIGCHLD is sent to the parent process. \\
Both parent and child processes independently execute the subsequent commands after the fork() system call.


\section{Process Termination}
\begin{itemize}
	\item All the resources held by process are released.
	\item All the information help in all data structures is removed.
	\item A process goes back to becoming a program and is stored on the secondary memory.
\end{itemize}


\section{Threads}
\begin{itemize}
	\item A thread is a part of a program.
	\item It is an execution unit within a process
	\item All threads of the same process share the same address space.
	\item All threas have separate stacks and individual Thread IDs.
	\item Thread is a lightweight process because: The contexxt switching between threads is inexpensive in terms of memory and resources.
	\item Even if 2 processes are communicating within each other, its is their threads that are communicating.
	\item They share the same process things like data, open files, descriptors, signals, current working directory, user and group id. 
	\item Each thread has a unique thread ID, which has a set of registers, stack for local variables, return addreses, priorities. 
\end{itemize}

There are 2 types of threads. This is similar to how there is always this binary existance of many basic OS operations and functions. We also had user and kernel spaces. 
\begin{enumerate}
	\item Kernel Level threads
	\item User level Threads. 
\end{enumerate}

\subsection{Differences between thread and processes}
\begin{enumerate}
	\item Process is program in execution, thread is process in execution
	\item Inter process communication is slower than inter thread communication.
	\item They both have unique ids, unique pid, and unique thread id.
	\item Context switching is expensive in processes, its inexpensive in thread.
	\item Every process has its own memory address, but threads use the memory of the process that they belong to.
\end{enumerate}

\subsection{User Level Threads}
\begin{enumerate}
	\item user level threads are implemented by users and the kernel is not aware of this existance of these threads. 
	\item kernel handles them as if they were single threaded processes. 
	\item User level threads are much faster than kernel level threads. 
	\item They are represented by a program counter, stack, registers and a small process control block. 
	\item Also there is no kernel involvement in synchronization for user elvel threads. 
	\item User level threads are managed entirely by the user level library. 
\end{enumerate}

\subsubsection*{Advantages of user level threads}
\begin{enumerate}
	\item User level threads are easier and faster to create than kernel elvel threads, so they can be more easily managed. 
	\item User level threads can be run on any operating system. 
	\item There are no kernel mode priviledges required for thread switching in user-level threads. 
\end{enumerate}

\subsubsection*{Disadvantages of user level threads}
\begin{enumerate}
	\item Multithreaded applications in user level threads cannot use multiprocessing to their advantage. 
	\item Entire process is blocked if one suer level thread persforms blocking operations. 
\end{enumerate}

\subsubsection*{Kernel level threads}
\begin{enumerate}
	\item Kernel level threads are handled by the operating system directly and thethread management is done by the kernel  
	\item context information for the proces as well as the process threads is all managed by the kernel. 
	\item Because of this kernel level gthreads are slower than user level threads.
\end{enumerate}


\section{Scheduling}

\begin{enumerate}
	\item Maximum CPU utilization obtained with multiprogramming. 
	\item CPU IO burst cycle - Process execution consists of a cycle of CPU execution and I/O wait. 
	\item This IO could be momory or something, it could also be the external device, and stuff. 
	\item The cycle looks something like :
	load store\\
	add store\\
	read from file\\
	WAIT FOR IO\\
	store increment\\
	index\\
	write to file\\
	WAIT FOR IO\\
	load store \\
	add store\\
	read from file \\
	WAIT FOR IO\\

	These are CPU and IO burst cycles. 

\end{enumerate}

\subsection{CPU or Process Scheduling}
There are 2 types of scheduling algorithms. 
\begin{enumerate}
	\item Non Preemptive: If the cpu allocated to a process, it keeps the CPU until the proess releases it by termiating or switching to waiting state.
	\item Pre Emptive: If the CPU allocated to a process, it may be released if high priority process needs the CPU.  
\end{enumerate}

\begin{itemize}
	\item It may take place in different parts
	\item The assigning of the task, or copying its states or something will be non premptive, so you cant mess with the CPU that time. 
	\item The actual task execution may be preemptive. 
\end{itemize}


\subsection{Scheduling Algorithms}

\begin{itemize}
	\item They deal with the problem of deciding whcih of the process in ready queue is to be allocated the CPU. Algo compared based on following criteria. 
	\item CPU utilization - Keeping the CPU as busy as possible
	\item Throughput - Number of processes completed or amount of wokr done per unit time. This has to be MAX
	\item Turnaround time - Time of submission of a process at the time of completion. This has to be MIN
	\item Waiting time - Amount of time a process has been waiting in the ready queue. 
	\item Response time - Amount of time it takes from when a request was submitted until the first response is produced. 
\end{itemize}

\subsection{Types of schedulers}
Scheduling is broken down into three categories: 
\begin{enumerate}
	\item Long Term Scheduling
	\begin{itemize}
		\item Is performed when a new process is created. 
		\item Long term scheduler or job scheduler selects which processes should be brought into the ready queue. 
		\item Long term scheduler is invoked very infrequently. in seconds or minutes. It may be slow too. 
		\item It controls the degree of multiprogramming. 
	\end{itemize}
	\item Medium Term Scheduling: 
	\begin{itemize}
		\item Part of the swapping function
		\item Swapping in decisions are taken by medium term scheduler. 
		\item Based on the need to anage the degree of multiprogramming.  
	\end{itemize}

	\item Short term scheduling
	\item Determines which ready processs will be assinge dht ecpu when it next becoems availabe and actually assigns the cpu to this proces. 
	\item Sort term scheduler or cpu scheduler selects which process should be executed next and allocatesd cpu
	\item short term scheduler is invoked very frequently. 
\end{enumerate}

\section{Scheduling Algorithms}
\subsection{First Come First Serve FSFC}

Note that this is non Preemptive, so it doesnt care as long as a process is in execution. 
\begin{enumerate}
	\item Selection function, max(w) : selects the process whcih is waiting in the ready queue for maximum time. 
	\item Decision Mode: Non Preemptive
	\item Throughput : Not Emphasized
	\item Response Time : It may be high, especially if there is a large variance in the process eeution times. 
	\item Overhead is Minimum : Theres not much logic involved.  
	\item Effect on Processes : Penalizes short processes. 
	\item Starvation is Not there. 
\end{enumerate}

Example: Processes P1, P2, P3 are there, P1 takes 24 Burst times, P2 takes 3, P3 takes 3. 
Waiting times: \\
P1 = 0;\\
P2 = 24;\\
P3 = 27;\\

Average Waiting time: $$\frac{(0 + 24 + 27)}{3} = 17 $$
Turnaround time for P1 = 24, P2 = 27, P3 = 30\\
Average Turnaround Time = $$\frac{(24 + 27 + 30)}{3} = 27 $$

If you include arrival time, then you have to include it in your calculations. Like you have to subtract it from the turnaround time to find the waiting time and stuff. 

\subsection{Shortest Job First Scheduling}

It associates with each process the length of its next cpu burst. Use these lengths to schedule the process with the shortest time. \\
There are 2 Schemes here. 
\begin{enumerate}
	\item Non Preemptive: Once CPU given to the process it cannot be preempted until completes its CPU burst.
	\item Preemptive -  If a new process arrives with CPU burst length less than remaining time of current exxecution process, Preempt it. This scheme is known as the Shortest Remaining Time First (SRTF).
	\item It is pretty optimal when it comes to saving the wait times. 
\end{enumerate}

\begin{enumerate}
	\item Selection Function: Minimum total service time required by the process, minus time spent in execution so far. 
	\item Decision mode: Preemptive (At Arrival time)
\end{enumerate}
\end{document}