% This is a Basic Assignment Paper but with like Code and stuff allowed in it, there is also url, hyperlinks from contents included. 

\documentclass[11pt]{article}

% Preamble

\usepackage[margin=1in]{geometry}
\usepackage{amsfonts, amsmath, amssymb}
\usepackage{fancyhdr, float, graphicx}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{fouriernc} % Use the New Century Schoolbook font
\usepackage[nottoc, notlot, notlof]{tocbibind}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{blindtext}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=cyan,
    pdfpagemode=FullScreen,
    }

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

% Header and Footer
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\textit{\Large{Philosophy of Science and Religion - Second Year B. Tech, Semester 2}}}
%\fancyhead[R]{\textit{something}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{1pt}



% Other Doc Editing
% \parindent 0ex
%\renewcommand{\baselinestretch}{1.5}

\begin{document}

\begin{titlepage}
	\centering

	%---------------------------NAMES-------------------------------

	\huge\textsc{
		MIT World Peace University
	}\\

	\vspace{0.75\baselineskip} % space after Uni Name

	\LARGE{
		Philosophy of Science and Religion\\
		Second Year B. Tech, Semester 1
	}

	\vfill % space after Sub Name

	%--------------------------TITLE-------------------------------

	\rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt}
	\rule{\textwidth}{0.6pt}
	\vspace{0.75\baselineskip} % Whitespace above the title



	\huge{\textsc{
		Importance of Spirituality in Human's Life and Pillars of Islam
		}} \\



	\vspace{0.5\baselineskip} % Whitespace below the title
	\rule{\textwidth}{0.6pt}\vspace*{-\baselineskip}\vspace*{2.8pt}
	\rule{\textwidth}{1.6pt}

	\vspace{1\baselineskip} % Whitespace after the title block

	%--------------------------SUBTITLE --------------------------	

	\LARGE\textsc{
		Assignment 1
	} % Subtitle or further description
	\vfill

	%--------------------------AUTHOR-------------------------------

	Prepared By
	\vspace{0.5\baselineskip} % Whitespace before the editors

	\Large{
		Sourab Karad \\
		Cyber Security and Forensics\\
		Batch A1, PA 39
	}


	\vspace{0.5\baselineskip} % Whitespace below the editor list
	\today
	
\end{titlepage}


\tableofcontents
\thispagestyle{empty}
\clearpage

\setcounter{page}{1}

\section{Question A}

\textbf{Importance of Spirituality in Human's Life}

It encourages people to have better relationships with themselves, others, and the unknown. Spirituality can help you deal with stress by giving you a sense of peace, purpose, and forgiveness. It often becomes more important in times of emotional stress or illness\\

Spirituality is a belief or a set of beliefs that helps people find a sense of purpose and meaning in their lives. It encourages people to have a better relationship with themselves, others, and the unknown. Spirituality can help people deal with stress by giving them a sense of peace, purpose, and forgiveness. This is especially important during times of emotional stress or illness when people may feel overwhelmed, anxious, or depressed.\\

One of the positive impacts of spirituality is that it can support mental health. People who are spiritual may feel a higher sense of purpose, peace, hope, and meaning in their lives. They may also experience better confidence, self-esteem, and self-control. Spirituality can help people make sense of their experiences in life and find a way to cope with difficult situations. When unwell, spirituality can help people feel inner strength and result in faster recovery.\\

Spirituality can also provide a sense of community and support. Those who are part of a spiritual community may feel a sense of belonging and may have more support from others. This can be especially helpful during difficult times when people need support and guidance from others who share their beliefs and values. Spirituality can also help people improve their relationships with themselves and others. It can help people develop a better understanding of themselves and their emotions, and it can help people cultivate empathy and compassion for others.\\

In conclusion, spirituality can have a positive impact on mental health and well-being. It can help people find a sense of purpose and meaning in their lives, cope with stress, and develop better relationships with themselves and others. By cultivating spirituality, people can experience a greater sense of peace, hope, and inner strength, and may feel more connected to something larger than themselves.\\
\clearpage

\section{Question B}


\subsection{What is the concept of Five pillars in Islam?}

The five pillars – the declaration of faith (shahada), prayer (salah), alms-giving (zakat), fasting (sawm) and pilgrimage (hajj) – constitute the basic norms of Islamic practice. They are accepted by Muslims globally irrespective of ethnic, regional or sectarian differences\\

Upholding the pillars is considered obligatory for all sincere followers of the Prophet Muhammad, male and female, Sunni and Shi‘a, but that doesn’t mean that all those who identify as Muslims keep them consistently. As in all religions, circumstances vary and some people are more committed than others. Such things as age, stage of life, work, family responsibilities, health and wealth all make a difference.\\

The Five Pillars of Islam are the basic acts of worship and the foundation of the Islamic faith. These practices are considered mandatory for every Muslim, and they are an essential part of their spiritual journey. The Five Pillars of Islam include Shahada, Salah, Zakat, Sawm, and Hajj.\\

Shahada is the first pillar of Islam, and it is the declaration of faith. It is a statement that there is no God but Allah, and Muhammad is his messenger. The Shahada is the fundamental belief that unites all Muslims, and it is the first step towards accepting Islam. By reciting the Shahada, a person becomes a Muslim, and they affirm their faith in Allah and his messenger.\\

Salah is the second pillar of Islam, and it refers to the five daily prayers that Muslims offer. These prayers are mandatory and are performed at specific times throughout the day. The prayers involve reciting verses from the Quran, standing, bowing, and prostrating. The act of Salah helps Muslims to connect with Allah and seek his guidance and blessings.\\

Zakat is the third pillar of Islam, and it refers to the act of giving to charity. Muslims are required to give a portion of their wealth to those in need. Zakat is a way to purify one's wealth and to help those who are less fortunate. This practice helps to create a sense of community and fosters a spirit of generosity among Muslims.\\

Sawm is the fourth pillar of Islam, and it refers to fasting during the holy month of Ramadan. Muslims are required to fast from sunrise to sunset, abstaining from food, drink, and other physical needs. Fasting is a way to purify one's body and soul and to increase one's awareness of Allah. It also helps to develop self-discipline and self-control.\\

Hajj is the fifth pillar of Islam, and it refers to the pilgrimage to the holy city of Mecca. It is mandatory for every able-bodied Muslim to perform Hajj at least once in their lifetime. The pilgrimage involves a series of rituals, including circumambulating the Kaaba, standing on the plain of Arafat, and throwing stones at the devil. The Hajj is a way to renew one's faith, seek forgiveness, and strengthen one's bond with Allah.\\

In conclusion, the Five Pillars of Islam are the foundation of the Islamic faith, and they are an essential part of every Muslim's spiritual journey. These practices help Muslims to connect with Allah, seek his guidance and blessings, and develop a sense of community and generosity.


\end{document}