% This is a Basic Assignment Paper but with like Code and stuff allowed in it, there is also url, hyperlinks from contents included. 

\documentclass[11pt]{article}

% Preamble

\usepackage[margin=1in]{geometry}
\usepackage{amsfonts, amsmath, amssymb}
\usepackage{fancyhdr, float, graphicx}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{fouriernc} % Use the New Century Schoolbook font
\usepackage[nottoc, notlot, notlof]{tocbibind}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{blindtext}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=cyan,
    pdfpagemode=FullScreen,
    }

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

% Header and Footer
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\textit{\Large{OOPJC Mini Project Report}}}
%\fancyhead[R]{\textit{something}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{1pt}



% Other Doc Editing
% \parindent 0ex
%\renewcommand{\baselinestretch}{1.5}

\begin{document}

\begin{titlepage}
	\centering

	%---------------------------NAMES-------------------------------

	\huge\textsc{
		MIT World Peace University
	}\\

	\vspace{0.75\baselineskip} % space after Uni Name

	\LARGE{
		Database Management Systems\\
		Second Year B. Tech, Semester 4
	}

	\vfill % space after Sub Name

	%--------------------------TITLE-------------------------------

	\rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt}
	\rule{\textwidth}{0.6pt}
	\vspace{0.75\baselineskip} % Whitespace above the title



	\huge{\textsc{
			Drawing of the Entity Relationship Diagram
		}} \\



	\vspace{0.5\baselineskip} % Whitespace below the title
	\rule{\textwidth}{0.6pt}\vspace*{-\baselineskip}\vspace*{2.8pt}
	\rule{\textwidth}{1.6pt}

	\vspace{1\baselineskip} % Whitespace after the title block

	%--------------------------SUBTITLE --------------------------	

	\LARGE\textsc{
		Assignment No. 1
	} % Subtitle or further description
	\vfill

	%--------------------------AUTHOR-------------------------------

	Prepared By
	\vspace{0.5\baselineskip} % Whitespace before the editors

	\Large{
		Krishnaraj Thadesar \\
		Cyber Security and Forensics\\
		Batch A1, PA 20
	}


	\vspace{0.5\baselineskip} % Whitespace below the editor list
	\today

\end{titlepage}


\tableofcontents
\thispagestyle{empty}
\clearpage

\setcounter{page}{1}

\section{Aim}

\section{Objectives}

\section{Problem Statement}
Requirements of the Company
The Company is organized into: 
\begin{enumerate}
    \item DEPARTMENTs. Each department has a name, number and an employee who manages the department. We keep track of the start date of the department manager. 
    \item Each department controls a number of PROJECTS. Each project has a name, Number, and is located at a single location. 
    \item We store each EMPLOYEEs social security number, address, salary, sex and birthdate. Each employee works for one department but may work on several projects. We keep track of the number of hours per week that an employee currently works on each project. We also keep track of the direct supervisor of each employee. 
    \item Each employee may have a number of DEPENDENTS. For each dependent we keep track of their name, sex, birthdate, and relationship to the employee.
\end{enumerate}

\section{Theory}

\subsection{Entities}
\begin{enumerate}
    \item Company - Department
    \item Department - Name, Number, Manager, Start Date
    \item Projects - Name, Number, Location
    \item Employees - SSN, Address, Salary, sex, Birthdate, Department, Supervisor, no. of hours per week.
    \item Dependents - Name, sex, birthdate, Relationship. 
\end{enumerate}


\section{Procedure}
\begin{enumerate}
    \item Ideentify the entities 
    \item Draw relationship table
    \item Draw rough er diagram.
    \item Draw each entity in depth, that have all the attributes. 
    \item Show the relationship with cardinality. If it is unary ternary etc. 
\end{enumerate}


\subsection{Relationships}
Relationships are mostly verbs, they are names of the columns.

\begin{enumerate}
	\item Department
\end{enumerate}


% \section{Platform}
% \textbf{Operating System}: Arch Linux x86-64 \\
% \textbf{IDEs or Text Editors Used}: Visual Studio Code with Jupyter\\
% \textbf{Interpreter}: python 3.10.8 \\

% \section{Pseudo Code or Algorithm}

% \section{Input}
% \section{Output}

% \section{Code}

% \subsection{Program}
% \lstinputlisting[language=C]{../Programs/Assignment_1.py}

% \subsection{Input and Output}
% \lstinputlisting[]{../Programs/Assignment_1_output.txt}

\section{Conclusion}

\clearpage

\section{FAQ}



\end{document}